### 2020-02-15 README.Rmd
Update README.Rmd

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/LiYingWang/kwl.pottery/master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/LiYingWang/kwl.pottery/master?urlpath=rstudio) [![R-CMD-check-compendium](https://github.com/LiYingWang/kwl.pottery/workflows/R-CMD-check-compendium/badge.svg)](https://github.com/LiYingWang/kwl.pottery/actions)
